### 2022-04-26 conclusion/conclusion.tex
more
future work

\chapter{Conclusion}
\setheader{Conclusion}
\label{ch:conclusion}

@@

As it is customary, we will conclude the thesis with some remarks about the
future work. \ehohii{} has been brought to the shape in which further
experimentation with higher-order superposition is possible. From the experience
gained in Chapters \ref{ch:bools} and \ref{ch:ho-techniques}, we can point out
dynamic clausification as the main feature that is not yet implemented. We plan
on implementing it in future.

In Chapter \ref{ch:ho-techniques} we only scratched the surface of finding
appropriate heuristics. Now that \ehohii{} implements more advanced higher-order
reasoning, it would be interesting to verify whether heuristics that are still not
ported are agnostic of the version of implemented higher-order superposition
calculus.

Some of the SAT-based techniques described in Chapter~\ref{ch:satfol} have been
implemented in E as well. However, this implementation is still in its early
phases as it is not properly tested and optimized. Verifying which techniques are
prover-agnostic would increase the confidence in them. We also started the work
of extending those techniques to full higher-order logic.

>>>>

\chapter{Conclusion and Future Work}
\setheader{Conclusion and Future Work}
\label{ch:conclusion}

@@

% As it is customary, we will conclude the thesis with some remarks about the
% future work. \ehohii{} has been brought to the shape in which further
% experimentation with higher-order superposition is possible. From the experience
% gained in Chapters \ref{ch:bools} and \ref{ch:ho-techniques}, we can point out
% dynamic clausification as the main feature that is not yet implemented. It is planned to implement it in the future.

% In Chapter \ref{ch:ho-techniques} we only scratched the surface of finding
% appropriate heuristics. Now that \ehohii{} implements more advanced higher-order
% reasoning, it would be interesting to verify whether heuristics that are still not
% ported are agnostic of the version of implemented higher-order superposition
% calculus.

% Some of the SAT-based techniques described in Chapter~\ref{ch:satfol} have been
% implemented in E as well. However, this implementation is still in its early
% phases as it is not properly tested and optimized. Verifying which techniques are
% prover-agnostic would increase the confidence in them. We also started the work
% of extending those techniques to full higher-order logic.

\section*{Future Work}

\looseness=-1
Even though the work in this thesis completes the three-step cycle, there are
still many unexplored alleys for future work. We separate them by the topic
explored in one of the earlier chapters:

\ourpara{Higher-Order Unification} The complete variant of unification procedure
described in Chapter \ref{ch:unif} is proved complete with substantial
restrictions on the order and kind of applied rules. To further
remove redundancy, we plan to find alternative, less explosive unification rules
that do not compromise completeness. Furthermore, we want to investigate if
there are more combinations of unification rules that lead to redundant unifiers
and find ways to remove those redundancy-inducing combinations.

We also described only one pragmatic variant of the unification procedure. This
variant was designed after we sifted through hundreds of benchmarks to get the
taste of what unifiers occur in practice. It is possible that this pragmatic variant
can be further tweaked to perform more efficiently without loosing many useful unifiers.

Lastly, we fixed the order in which Zipperposition applies different unification
rules. It would be interesting to see if applying imitation before projection
(or vice versa) yields performance improvements on some kinds of problems. 
We also postponed the application of the most explosive rules such as iteration
to the very end. However, it would not be surprising that there are many hard hand-crafted
problems on which applying these rules would lead to a proof more quickly.

\ourpara{Pragmatic Techniques and Heuristics } Many of the Boolean reasoning
techniques described in Chapter \ref{ch:bools} were either inspired by the ones
implemented in traditional higher-order theorem provers or by the unsolved TPTP
benchmarks. Since the work present in Chapter \ref{ch:bools} anticipated the
complete higher-order calculus that could make these techniques obsolete, we
implemented only the most successful ones that are easy to port to
saturation-based provers.  Most notably, unlike Satallax
\cite{cb-2013-satallax}, Zipperposition does not use the fact that there only
finitely many functions of a type built only using function type constructor
($\rightarrow$) and Boolean type ($o$). Implementing techniques for efficient
enumeration of all Boolean functions of a given type could help Zipperposition
prove problems that are still out of its reach, but can be solved by Satallax.

In Chapter \ref{ch:ho-techniques} we explored how we keep the explosion inherent
to \osup{} calculus under control. Due to time and resource
constraints, in the evaluation of our new given-clause loop we left some
parameters that control which streams are queried fixed. We plan to tune these
parameters in the future.  Similarly, we provided only some of the clause
priority functions that rely on higher-order features. We plan to investigate
more proofs in detail to create new priority functions that more cautiously
separate less and more useful higher-order inferences. Lastly, we observed that
use of Ehoh as a backend greatly improves the performance of Zipperposition. We
plan to further investigate the proofs that Ehoh returns and find out how
Zipperposition can find them without the use of a backend.

\ourpara{Further Extensions of \ehohii{}} \ehohii{} outperforms other provers on
problems coming proof assistants. However, its performance on TPTP problems is
slightly behind Zipperposition. We plan to further investigate the benchmarks on
which \ehohii{} fails, but are proved by Zipperposition. One of the first
features we plan implement is dynamic clausification, which can possibly help
improve \ehohii{}'s performance on first-order problems as well. We also plan to
experiment with implementing some of the \osup{} rules necessary for
completeness such as \infname{FluidSup}. Heuristics of \ehohii{} are trained on
a subset of Sledgehammer and TPTP problems. We plan to use other benchmark sets
such as GRUNGE to make \ehohii{} efficient on a wider range of higher-order
benchmarks.

\ourpara{SAT-inspired eliminations for superposition} We already implemented
some of the techniques described in Chapter~\ref{ch:satfol} in E. However, this
implementation is not properly tested and optimized. We plan to put finishing
touches to this implementation and test the effects of implemented preprocessing
techniques on E's performance. There are more techniques used in SAT solving,
notably bounded variable addition \cite{mhb-12-reencoding} and blocked clause
addition \cite{ok-99-er}, that we did not port to first-order logic. We want to
investigate if these techniques can be lifted to first-order logic. Lastly, we
already started work on porting existing techniques to higher-order logic.
